Measuring contrast processing in the visual system using SSVEP (and VEP?)

### 2024-03-29 review.qmd
Zotero integration

Measuring the SSVEP at multiple levels was made faster by the development of the ‘sweep VEP’ paradigm in which the stimulus changed its contrast, spatial frequency or some other property, throughout a trial [Tyler, Nakayama etc 1979]. To avoid hysteresis effects, the sweep is sometimes conducted both up and down in the same experiment [Tyler, Norcia etc: 1985, 1990 etc]. This general approach revealed much about the development of visual abilities in infants [@braddick], as well as deficits in neurological disease.

In general, SSVEP measurements of infant vision have revealed that the development of spatial acuity for both achromatic and chromatic contrast as well as stereoscopic depth perception is faster than had been supposed previously based on behavioural readouts [@DobsonTeller78, @NorciaTyler85, @NorciaGerhard 15]. At least some of this difference is likely due to the high SNR of the SSVEP technique.

>>>>

Measuring the SSVEP at multiple levels was made faster by the development of the ‘sweep VEP’ paradigm in which the stimulus changed its contrast, spatial frequency or some other property, throughout a trial [Tyler, Nakayama etc 1979]. To avoid hysteresis effects, the sweep is sometimes conducted both up and down in the same experiment [Tyler, Norcia etc: 1985, 1990 etc]. This general approach revealed much about the development of visual abilities in infants [@braddick, @atkinson]. In general, SSVEP measurements of infant vision have revealed that the development of spatial acuity for both achromatic and chromatic contrast as well as stereoscopic depth perception is faster than had been supposed previously based on behavioural readouts [@dobsonVisualAcuityHuman1978; @norciaSpatialFrequencySweep1985, ]. At least some of this difference is likely due to the high SNR of the SSVEP technique.
